---
title: "Week1-Code-Excerise"
format:
  html:
    theme: flaty
editor: visual
execute: 
  warning: false
  message: false
---

### Task

Understanding the descriptive statistics for `airquality`

```{r}

library(tidyverse,warn.conflicts = FALSE,verbose = FALSE)
library(skimr)
library(gtExtras)
library(svglite)
library(corrplot,warn.conflicts = FALSE)
library(knitr)

airquality_tbl <- airquality |> as_tibble()
```

-   Calculate the mean of the Temp column in the `airquality` data set. What is the mean temperature?

-   What is the median value of the Temp column?

-   What is the range of values in the Temp column?

-   Calculate the variance of the Wind column. What is the variance?

-   Calculate the standard deviation of the Wind column. What is the result?\

```{r}

airquality_tbl |> 
    reframe(avg_temp = mean(Temp),
              median_temp = median(Temp),
              range_temp = toString(range(Temp)),
              wind_var = var(Wind),
              wind_std_dev = sqrt(var(Wind))
              )

```

### Summary statistics

```{r}

airquality_tbl |> 
    skim() |> 
    kable()
```

```{r}
gt_plt_summary(airquality_tbl)

```

### correlation matrix plot

```{r}
corrplot(cor(airquality_tbl,
  use = "pairwise.complete.obs"), method = 'square',
  addCoef.col = "red"
  
)
```
