---
title: "week2-sampling-methods-exercise"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(janitor)

set.seed(35867)                                            # Set seed for reproducibility
 
my_synt <- tibble (ID = 1:200,                          # Create a self-defined data
  Age = sample(18:65, 200, replace = TRUE),
  Gender = sample(c("Male", "Female", "Other"), 200, replace = TRUE),
  Income = sample(20000:100000, 200, replace = TRUE),
  Department = sample(c("Sales", "HR", "IT", "Finance"), 200, replace = TRUE))
 

```

## Simple random sampling

### Without replacement

1.  Perform simple random sampling without replacement, selecting 15 rows from your data set.

```{r}

my_synt |> 
    sample_n(size = 15,replace = FALSE )



```

### With replacement

2.Perform simple random sampling with replacement, selecting 25 rows from your data set.

```{r}

my_synt |> 
    sample_n(size = 15,replace = TRUE )


```

3.  Calculate the mean income of all individuals in your data set, and compare it with the mean income of a random sample of size 50 taken with replacement.

```{r}

my_synt_srwrs_50 <- my_synt |> 
    sample_n(size = 50 ,replace = TRUE)


my_synt_srwrs_50 |> 
    summarize(avg_income_sample = mean(Income,na.rm= TRUE)) |> 
    cbind(
my_synt|> 
    summarize(avg_income_pop = mean(Income,na.rm= TRUE)))


```

4.Implement systematic sampling on your data set.
Select a random starting point and a sampling interval of 7.

```{r}
my_synt_syst <- my_synt |> 
  slice(seq(
    sample(1:7, 1), # Random starting point
    nrow(my_synt),
    by = 7
  ))

my_synt_syst
```

5.Group your data by the `Gender` column and perform stratified sampling, selecting 40% of the observations from each gender group.

```{r}


my_synt |>
  tabyl(Gender) 

```

```{r}
my_synt_stra <- my_synt |> 
    group_by(Gender) |> 
    sample_frac(size = 0.4) |> 
    ungroup()

my_synt_stra
```

```{r}
my_synt_clust <- my_synt %>%                              
  filter(Department %in% sample(unique(Department), 3))
my_synt_clust                                           
```
