---
title: "Week3 - Exercise"
format: html
editor: visual
---

```{r,warning=True}
library(tidyverse)
library(fs)
library(broom)
library(janitor)
library(ggiraphExtra)

data_path <- fs_path('data')

students_tbl <- read_csv(data_path / 'StudentsPerformance.csv')

students_tbl <- students_tbl |> clean_names()

students_tbl |> 
    head()
```

1.  Subset the `math.score` column by gender, creating two separate vectors: one for male students and one for female students.

2.  Calculate the mean math scores for both male and female students.

3.  Perform Welch’s t-test to check if there is a statistically significant difference between the math scores of male and female students.

```{r}

students_tbl|>
  group_by(gender) |>
  summarise(avg_math_score = math_score |> mean())

```

```{r}
students_tbl|>
  group_by(gender) |>
  nest() |>
  mutate(shapiro = map(data, ~ tidy(shapiro.test(.x$math_score)))) |>
  unnest(shapiro)
```

normal test is fine with respect to gender

```{r}

t.test(math_score ~ gender, data = students_tbl) |> tidy()

```

s t-test shows a p-value of 8.421e-08, indicating a significant difference between the math scores of male and female students.

4.  Perform an F-test using the `var.test()` function to check whether the variances of the math scores for male and female students are equal.
5.  Perform Student’s t-test using `var.equal = TRUE` in the `t.test()` function, assuming equal variances, to compare the math scores between male and female students. Compare the results with Welch’s t-test. Are there any notable differences in the p-values or conclusions drawn from the two tests?

```{r}


var.test(math_score ~ gender, data = students_tbl) |> tidy()

```

a p-value of 0.09016, indicating no significant difference in variances between the two groups.

```{r}

t.test(math_score ~ gender, data = students_tbl,var.equal= TRUE) |> tidy()

```

Student’s t-test gives a p-value of 9.12e-08, which is similar to the Welch’s t-test result.
Both tests indicate a significant difference between the groups, with slightly different degrees of freedom and confidence intervals

```{r}
students_tbl |> 
    tabyl(parental_level_of_education)

```

```{r}
students_tbl <- students_tbl |> 
    mutate(parental_level_of_education = as_factor(parental_level_of_education))

levels(students_tbl$parental_level_of_education) <- c('BA','C','MA','AD','HS','SHS')

```

```{r}

anvoa_ple <- aov(math_score~ parental_level_of_education,students_tbl)

anvoa_ple |> tidy()
```

ANOVA test results in a p-value of 5.59e-06, indicating that the parental level of education significantly affects the math scores.

```{r}

tukey_ple <- TukeyHSD(anvoa_ple,ordered = TRUE)                      # Perform Tukey's HSD test
tukey_ple 

```

```{r}
ggHSD(tukey_ple,no = 1, digits = 2, interactive = FALSE)
```

10. Plot the residuals of the ANOVA model to check the normality assumption using the `plot()` function.

```{r}
plot(anvoa_ple,2)
```

Deviations from the line may indicate violations of the normality assumption.

11. Create a contingency table showing the relationship between parental education level and type of lunch provided (standard or free/reduced).

```{r}
student_cross_tbl <- students_tbl |> 
    tabyl(parental_level_of_education,lunch)

student_cross_tbl

```

12. Perform a Chi-squared test on the contingency table to test for independence between parental education level and type of lunch.

13. Print the expected counts from the Chi-squared test to compare with the observed counts

```{r}
chi_square_gt <- chisq.test(student_cross_tbl)               # Perform Chi-Squared test
chi_square_gt |> tidy()                                        # Print Chi-Squared test results
```

a p-value of 0.9531, indicating that there is no significant association between parental education level and the type of lunch provided.

```{r}
chi_square_gt$expected
```
